---
title: "Chap 1 Rmarkdown"
author: "Elvira Lucas"
date: "2023-02-17"
output: 
  html_document: 
    theme: flatly
    highlight: tango
editor_options: 
  chunk_output_type: console
params:
  Joueur: Ronaldo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Head1

Paramètres : `r params$Joueur`

## Head2

> When the solution is simple, God is answering.

> ***LIST OF RESULTS***
>
> -   Result 1
> -   Result 2
>
> Everything looks good.

The following is a comment, <!-- THIS IS MY COMMENT --> so it will not be displayed in the final output document.

The fowling paragrapher is commented out, <!-- 
THIS IS MY COMMENT 1
THIS IS MY COMMENT 2
--> so nothing is shown.

Options for knittr::kable :

  - col.names
  - align : can be used with several letter inclosed inside "", e.g. align = "lcclr" for left,center,center,left,right
  - caption
  - digits: can be a vector for each column (e.g. digits = c(2,3,4,4))
  - To use math expression, set ´escape´ to FALSE and use`$`inside the "" (use double \ before like "$\\beta_0$")
  - If you want several tables side by side, use a list of the different data.frames (kable(list(tab1,tab2), options...))

When we want to switch the NA from the table for sth else, use ´options(knitr.kable.NA="sth else")´

```{r, rows.print=5}
head(cars) |>
  knitr::kable(
    caption = "First six observation in 'cars' data",
    col.names = c("Speed of cars", "Distances taken to stop")) |>
  kableExtra::kable_styling()
```

Options for kableExtra::kbl/kable_...:

  * bootstrap_options : vector of options :
      * striped : add striped lines
      * hover : add highlighting 
     * condensed
  * full_width 
  * position : position of the table and if you use float_right/left, the text appear beside
  * font_size
  * fixed_header : the header follows the page, to change color, use list(enabled=T, background = "color")
  * add_header_above
  * pack_rows : group rows pack_rows("name", first row, last row)
  * Scroll_box : options width and height

Options for DT::data_table:

  * editable = "cell" : allow editing the value inside the cells, specification :
     * editable = list(target = 'row', disable = list(columns = c(1, 3, 4)) to specify which columns
  * row.names : logical
  * colnames : vector, colnames = c('A Better Name' = 'Sepal.Width') to specify which column name to change (or use the number, 1 to the             row names)
  * caption
  * filter : add a filter with option "top" or "bottom"
  * fillcontainer: logical, fill the container or not in the space
  * options : list of :
    * dom = 'lftipr' to add this options in the table where :
      * l : length changing input control
      * f : filtering input
      * t : The table!
      * i : Table information summary
      * p : pagination control
      * r : processing display element
    * pagelength : the length of the table when show
    * lengthMenu : vector with the proposed length of the table
    * scrollX ou scrollY : in "000px", to change the size of the scrolling box

```{r}
mtcars |>
  DT::datatable(
    filter = "top",
    options = list(pageLength = 5, scrollX = TRUE, dom = "ltp"))
```

```{r}
head(cars) |>
  knitr::kable(
    caption = "This is the six first rows of the iris data",
    col.names = c("Speed of cars", "Distances taken to stop")
  )
```

```{r}
iris2 <- head(iris)
knitr::kable(iris2, col.names = gsub("[.]", " ", names(iris)))
```

