---
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
 
```{r}
title <- "Type a title"
```

#### How to use this app

Start by choosing a number, say $\mu$, using the slider below labeled "_Choose a mean_" (default value $0$). 
One done, two random samples of size $10$ each will be generated. 

As a result, you get two tabs:

* _**Data and Summary**_ with (i) the generated data frame, and (ii) its summary, and
* _**Plot**_ with a Scatter plot of the data.  

You can then introduce a title of your choice for the plot. 

---

```{r, UiInputs}

textInput <- textInput(
  inputId = "inp1a",
  label = NULL,
  placeholder = title
)

sliderInput <- sliderInput(
  inputId = "inp2a",
  label = "Choose a mean",
  value = 0, min = -30, max = 30
)
```

```{r, ReacVariables}
dt <- reactive({
  m <- input$inp2a
  X <- rnorm(10, mean = m)
  Y <- 1 + 2 * X + rnorm(10, sd = 0.2)
  data.frame(X, Y)
})
```

```{r, Outputs}
TableOut <- renderTable(dt())
PrintOut <- renderPrint(dt() |> summary())
PlotOut <- renderPlot(plot(Y ~ X, data = dt(), main = input$inp1a))
```

```{r, Layout}
sidebarPanel(
  textInput,
  sliderInput,
)

mainPanel(
  tabsetPanel(
    tabPanel(
      title = "Data and Summary",
      column(4, TableOut),
      br(),
      column(8, PrintOut)
    ),
    tabPanel(
      title = "Plot",
      PlotOut
    )
  )
)
```

```{r, mean.dif}
mean.dif <- renderText(round(mean(dt()$X) - mean(dt()$Y), 3))
```

Note that the different in the means between $X$ and $Y$ is 
`r mean.dif`. 